Forschungsprojekt

### 2020-06-29 documentation/paper/main.tex
doc

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
%\usepackage{csquotes}
\usepackage{hyperref}

\bibliography{literature.bib}
\title{Forschungsprojekt}
\author{Simon König (3344789) \\ \and Leon Matzner (3315161) \\ \and Felix Rollbühler (3310069) \\ \and Jakob Schmid (??????)}
\date{\today}

@@

\section{Things}
\input{galois.tex}

\input{polymer.tex}

@@

>>>>

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
%\usepackage{csquotes}
\usepackage{hyperref}
\usepackage{amsmath}

\bibliography{literature.bib}
\title{Forschungsprojekt}
\author{Simon König (3344789) \and Leon Matzner (3315161) \and Felix Rollbühler (3310069) \and Jakob Schmid (??????)}
\date{\today}

@@

\input{graphFormats}
\section{Things}
\input{galois}

\input{polymer}

@@

\bibitem{adjListFormat}
\BIBentryALTinterwordspacing
J.~Shun, G.~Blelloch, J.~Fineman, P.~Gibbons, A.~Kyrola, K.~Tangwonsan, and
  H.~V. Simhadri. (2020, Jun.) {Problem Based Benchmark Suite}. graphIO.html.
  [Online]. Available: \url{http://www.cs.cmu.edu/~pbbs/benchmarks/}
\BIBentrySTDinterwordspacing
